My JuliaCon proceeding

### 2023-06-02 paper.tex
change unicode -> to tex

There are a few exceptions to the rule of ``NaN in and no NaN out → kill''---some instances that we report as being a NaN kill might be instead a \emph{NaN-repair}, i.e. where the user explicitly checks for a NaN and gets some non-NaN value as a result.
Once clear instance of this is the \texttt{isnan} function.
Calling \texttt{isnan} and getting a boolean is expected behavior, and is usually used in error handling or in \emph{explicit} handling of unexpected values.
FloatTracker still reports these cases in the kill logs so as to be complete---the user must not blindly assume that every instance of a NaN kill is bad and might be a case of NaN repair.

>>>>

There are a few exceptions to the rule of ``NaN in and no NaN out $\rightarrow$ kill''---some instances that we report as being a NaN kill might be instead a \emph{NaN-repair}, i.e. where the user explicitly checks for a NaN and gets some non-NaN value as a result.
Once clear instance of this is the \texttt{isnan} function.
Calling \texttt{isnan} and getting a boolean is expected behavior, and is usually used in error handling or in \emph{explicit} handling of unexpected values.
FloatTracker still reports these cases in the kill logs so as to be complete---the user must not blindly assume that every instance of a NaN kill is bad and might be a case of NaN repair.
